### 2022-10-12 ersteops/templates/printpdf/rendered_template.tex
add little template strategy for emergency grade
fix ui spinner

    %Times
    \put(0.03117976,0.58432043){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 2022-07-22\end{tabular}}}}%
    \put(0.06427789,0.58446308){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
    \put(0.10029604,0.58387567){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
    \put(0.13910523,0.58360406){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
    \put(0.17543913,0.58380438){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 00:07\end{tabular}}}}%

    \put(0.37115545,0.5742565){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%

@@

    \put(0.10902655,0.55515604){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 11\end{tabular}}}}%
    \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Basica\end{tabular}}}}%
    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ABC-123\end{tabular}}}}%

    %Paciente
    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize F55 - Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%
    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 12\end{tabular}}}}%
    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%

>>>>

    %Times
    \put(0.03117976,0.58432043){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 2022-07-22\end{tabular}}}}%

    \put(0.06427789,0.58446308){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%

    \put(0.10029604,0.58387567){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%

    \put(0.13910523,0.58360406){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%

    \put(0.17543913,0.58380438){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 00:07\end{tabular}}}}%

      \put(0.37115545,0.574256){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X\end{tabular}}}}%

@@

    \put(0.10902655,0.55515604){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 11\end{tabular}}}}%
    \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny Basica\end{tabular}}}}%
    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ABC-123\end{tabular}}}}%

    %Paciente
    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny F55 - Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%
    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 12\end{tabular}}}}%
    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
